\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-02-01 paper.qmd
Update the repo

```{r}
#| echo: false
#| label: fig-binsize
#| fig-pos: H
#| fig-cap: "Hexbin plots from different number of bins for the **UMAP** projections of **S-curve** data: (a) b = 32 (4, 8), s = 1.643542, (b) b = 264 (12, 22), s = 1.643542, and (c) b = 840 (21, 40), s = 1.643542. The hexbins are colored based on the density of points, with darker colors indicating higher point density and yellow color representing lower point density within each bin. What is the number of bins that would be effective in representing low-dimensional data?"

@@

mse_plot <- ggplot(MSE_df |> dplyr::filter(method == "UMAP"), aes(x = number_of_bins,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("Total number of bins")

```{r}
#| echo: false
#| fig-cap: "Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset. What is the most effective NLDR technique to represent the original data in a 2D space? What is the effective number of bins in each NLDR technique to create a 2D model?"
#| label: fig-diagnosticpltScurve
##| out-width: 100%

@@

hex_full_count_df_loop2 <- hex_full_count_df_loop2 |>
  dplyr::mutate(type = if_else(std_counts < 0.12, "low", "high"))

@@

num_bins_umap_s_curve <- 11
shape_val_umap_s_curve <- calculate_effective_shape_value(.data = UMAP_s_curve,
                                                          x = UMAP1, y = UMAP2) ## 1.259938
## To extract bin centroids
hexbin_data_object_umap_s_curve <- extract_hexbin_centroids(nldr_df = UMAP_s_curve, num_bins = num_bins_umap_s_curve, shape_val = shape_val_umap_s_curve, x = UMAP1, y = UMAP2)

@@

df_bin_centroids_umap_s_curve <- df_bin_centroids_umap_s_curve |>
  dplyr::filter(std_counts > 0.12)

@@

## To draw with AIC
aic_plot_lwd <- ggplot(MSE_df_lwd |> dplyr::filter(data_type == "training") |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_hex,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("Benchmark value")
## Effective number of bins along x-axis

mse_plot_lwd <- ggplot(MSE_df_lwd |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_hex,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("Benchmark value")

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset with different benchmark values to remove the low-density heaxgons. What is the effective benchmark value to remove the low-density heaxgons?"
#| label: fig-diagnosticpltScurvelwd
##| out-width: 100%

@@

@@

@@

## To draw with AIC
aic_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("Benchmark value")
## Effective number of bins along x-axis

mse_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("Benchmark value")

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset with different benchmark values to remove the long edges. What is the effective benchmark value to remove the long edges?"
#| label: fig-diagnosticpltScurvelgrm
##| out-width: 100%

@@

$$
\text{MSE} = \sum_{j = 1}^{n} \frac{\sqrt{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}}{n}
$$ {#eq-equation9}

@@

## To draw with AIC
aic_gau_plot <- ggplot(MSE_df_gau |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                                                             y = total_error,
                                                             color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("Total number of bins")
## Effective number of bins along x-axis

mse_gau_plot <- ggplot(MSE_df_gau, aes(x = number_of_bins,
                   y = total_mse,
                   color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("Total number of bins")

@@

aic_gau_plot + mse_gau_plot +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

>>>>

```{r}
#| echo: false
#| label: fig-binsize
#| fig-pos: H
#| fig-cap: "Hexbin plots from different number of bins for the **UMAP** projections of **S-curve** training data: (a) b = 32 (4, 8), s = 1.643542, (b) b = 264 (12, 22), s = 1.643542, and (c) b = 840 (21, 40), s = 1.643542. The hexbins are colored based on the density of points, with darker colors indicating higher point density and yellow color representing lower point density within each bin. What is the number of bins that would be effective in representing low-dimensional data?"

@@

mse_plot <- ggplot(MSE_df |> dplyr::filter(method == "UMAP"), aes(x = number_of_bins,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
   geom_vline(xintercept = 144, linetype="dashed", 
                color = "red", size=0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("Total number of bins")

```{r}
#| echo: false
#| fig-cap: "Goodness of fit statistics from UMAP applied to training S-curve dataset. What is the effective number of bins in each NLDR technique to create a 2D model? The MSE plot have a steep slope at the beginning, indicating that a smaller number of bins causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of bins generates a smaller error. Using the elbow method, when the total number of bins is set to 144, the slope of the Mean Squared Error (MSE) plot experiences a sudden and noticeable change, resembling an elbow-like shape. This point indicates that adding less bins does not enough to capture the data structure."
#| label: fig-diagnosticpltScurve
##| out-width: 100%

@@

hex_full_count_df_loop2 <- read_rds("data/s_curve/s_curve_hex_8.rds")

hex_full_count_df_loop2 <- hex_full_count_df_loop2 |>
  dplyr::mutate(type = if_else(std_counts <= 0.20, "low", "high"))

@@

num_bins_umap_s_curve <- 8
shape_val_umap_s_curve <- calculate_effective_shape_value(.data = UMAP_s_curve,
                                                          x = UMAP1, y = UMAP2) ## 1.259938
## To extract bin centroids
hexbin_data_object_umap_s_curve <- extract_hexbin_centroids(nldr_df = UMAP_s_curve, num_bins = num_bins_umap_s_curve, shape_val = shape_val_umap_s_curve, x = UMAP1, y = UMAP2)

@@

df_bin_centroids_umap_s_curve <- df_bin_centroids_umap_s_curve |>
  dplyr::filter(std_counts > 0.20)

@@

## To draw with AIC
aic_plot_lwd <- ggplot(MSE_df_lwd |> dplyr::filter(data_type == "training") |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_hex,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("benchmark value")
## Effective number of bins along x-axis

mse_plot_lwd <- ggplot(MSE_df_lwd |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_hex,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 0.2, linetype="dashed", 
                color = "red", size=0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("benchmark value")

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Goodness of fit statistics from UMAP applied to training S-curve dataset with different benchmark values to remove the low-density heaxgons. What is the effective benchmark value to remove the low-density heaxgons? The MSE plot have a steep slope at the beginning, indicating that a smaller benchmark causes a small amount of error. Then, the slope gradually increases or level up, indicating that a higher number of benchmark values generates a higher error. Using the reverse elbow method, when the benchmark value is set to 0.2, the slope of the Mean Squared Error (MSE) plot experiences a sudden and noticeable change, resembling an elbow-like shape. This point indicates that higher benchmark values remove the necessary bins as well which lead to distruct the 2D structure."
#| label: fig-diagnosticpltScurvelwd
##| out-width: 100%

@@

num_bins_umap_s_curve <- 8
shape_val_umap_s_curve <- calculate_effective_shape_value(.data = UMAP_s_curve,
                                                          x = UMAP1, y = UMAP2) ## 1.259938
## To extract bin centroids
hexbin_data_object_umap_s_curve <- extract_hexbin_centroids(nldr_df = UMAP_s_curve, num_bins = num_bins_umap_s_curve, shape_val = shape_val_umap_s_curve, x = UMAP1, y = UMAP2)

@@

## To find the benchmark value
benchmark_umap_s_curve <- find_benchmark_value(.data = distance_umap_s_curve, distance_col = distance)
benchmark_umap_s_curve <- 1.346694

@@

## To draw with AIC
aic_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_point(data = error_df_lg |> dplyr::filter(method == "UMAP") |> filter(benchmark_rm_lg == 1.347), aes(x = benchmark_rm_lg,
                                       y = total_error
),
                                       color = "#e41a1c") +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("benchmark value")
## Effective number of bins along x-axis

mse_plot_lg <- ggplot(error_df_lg |> dplyr::filter(method == "UMAP"), aes(x = benchmark_rm_lg,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_point(data = error_df_lg |> dplyr::filter(method == "UMAP") |> filter(benchmark_rm_lg == 1.347), aes(x = benchmark_rm_lg,
                                       y = total_mse
),
                                       color = "#e41a1c") +
  geom_line() +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#377eb8", "#e41a1c", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("benchmark value")

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Goodness of fit statistics from UMAP applied to training S-curve dataset with different benchmark values to remove the long edges. What is the effective benchmark value to remove the long edges? $1.347$ is the chosen benchmark value to remove long edges. The value is selected through a visual inspection of the triangular mesh is conducted to verify whether it successfully eliminates long edges."
#| label: fig-diagnosticpltScurvelgrm
##| out-width: 100%

@@

$$
\text{MSE} = \sum_{j = 1}^{n} \frac{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}{n}
$$ {#eq-equation9}

@@

## To draw with AIC
aic_gau_plot <- ggplot(MSE_df_gau |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                                                             y = total_error,
                   color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_colour_manual(values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("AIC") +
  xlab("total number of bins") + 
  facet_wrap(vars(method), ncol = 5)
## Effective number of bins along x-axis

mse_gau_plot <- ggplot(MSE_df_gau, aes(x = number_of_bins,
                   y = total_mse,
                   color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_colour_manual(values = c("#e41a1c", "#377eb8", "#4daf4a", "#984ea3", "#ff7f00")) +
  ylab("MSE") +
  xlab("total number of bins") + 
  facet_wrap(vars(method), ncol = 5)

@@

aic_gau_plot + mse_gau_plot +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', nrow = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

### 2024-02-01 paper.tex
Update the repo

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-binsize}Hexbin plots from different number of bins
for the \textbf{UMAP} projections of \textbf{S-curve} data: (a) b = 32
(4, 8), s = 1.643542, (b) b = 264 (12, 22), s = 1.643542, and (c) b =
840 (21, 40), s = 1.643542. The hexbins are colored based on the density
of points, with darker colors indicating higher point density and yellow
color representing lower point density within each bin. What is the
number of bins that would be effective in representing low-dimensional
data?}

@@

\caption{\label{fig-diagnosticpltScurve}Goodness of fit statistics from
different NLDR techniques applied to training S-curve dataset. What is
the most effective NLDR technique to represent the original data in a 2D
space? What is the effective number of bins in each NLDR technique to
create a 2D model?}

@@

\caption{\label{fig-diagnosticpltScurvelwd}Goodness of fit statistics
from different NLDR techniques applied to training S-curve dataset with
different benchmark values to remove the low-density heaxgons. What is
the effective benchmark value to remove the low-density heaxgons?}

@@

\caption{\label{fig-diagnosticpltScurvelgrm}Goodness of fit statistics
from different NLDR techniques applied to training S-curve dataset with
different benchmark values to remove the long edges. What is the
effective benchmark value to remove the long edges?}

@@

\begin{equation}\protect\hypertarget{eq-equation9}{}{
\text{MSE} = \sum_{j = 1}^{n} \frac{\sqrt{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}}{n}
}\label{eq-equation9}\end{equation}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, enhanced, sharp corners, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-binsize}Hexbin plots from different number of bins
for the \textbf{UMAP} projections of \textbf{S-curve} training data: (a)
b = 32 (4, 8), s = 1.643542, (b) b = 264 (12, 22), s = 1.643542, and (c)
b = 840 (21, 40), s = 1.643542. The hexbins are colored based on the
density of points, with darker colors indicating higher point density
and yellow color representing lower point density within each bin. What
is the number of bins that would be effective in representing
low-dimensional data?}

@@

\caption{\label{fig-diagnosticpltScurve}Goodness of fit statistics from
UMAP applied to training S-curve dataset. What is the effective number
of bins in each NLDR technique to create a 2D model? The MSE plot have a
steep slope at the beginning, indicating that a smaller number of bins
causes a larger amount of error. Then, the slope gradually declines or
level off, indicating that a higher number of bins generates a smaller
error. Using the elbow method, when the total number of bins is set to
144, the slope of the Mean Squared Error (MSE) plot experiences a sudden
and noticeable change, resembling an elbow-like shape. This point
indicates that adding less bins does not enough to capture the data
structure.}

@@

\caption{\label{fig-diagnosticpltScurvelwd}Goodness of fit statistics
from UMAP applied to training S-curve dataset with different benchmark
values to remove the low-density heaxgons. What is the effective
benchmark value to remove the low-density heaxgons? The MSE plot have a
steep slope at the beginning, indicating that a smaller benchmark causes
a small amount of error. Then, the slope gradually increases or level
up, indicating that a higher number of benchmark values generates a
higher error. Using the reverse elbow method, when the benchmark value
is set to 0.2, the slope of the Mean Squared Error (MSE) plot
experiences a sudden and noticeable change, resembling an elbow-like
shape. This point indicates that higher benchmark values remove the
necessary bins as well which lead to distruct the 2D structure.}

@@

\caption{\label{fig-diagnosticpltScurvelgrm}Goodness of fit statistics
from UMAP applied to training S-curve dataset with different benchmark
values to remove the long edges. What is the effective benchmark value
to remove the long edges? \(1.347\) is the chosen benchmark value to
remove long edges. The value is selected through a visual inspection of
the triangular mesh is conducted to verify whether it successfully
eliminates long edges.}

@@

\begin{equation}\protect\hypertarget{eq-equation9}{}{
\text{MSE} = \sum_{j = 1}^{n} \frac{\sum_{i = 1}^{p} (x_{ij} - C_{x_ij})^2}{n}
}\label{eq-equation9}\end{equation}
